Social and Economic Changes have decreased birth rates for millenial and Gen z Mothers (Work in progress)

### 2022-02-26 Output/paper 2.Rmd
Created new files, edited code and writing

---
title: "Social and Economic Changes have decreased birth rates for millenial and Gen z Mothers (Work in progress)"
author: "Olaedo Okpareke, Arsh"
thanks: 'Code and data are available at: https://github.com/OlaedoOkpareke/Paper2Repository. DOI link:' 
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "PUT SOMETHING HERE"
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references2.bib

>>>>

---
title: "Social and Economic Changes have decreased birth rates for millenial and Gen z Mothers (Work in progress)"
author: "Olaedo Okpareke, Arsh"
thanks: 'Code, data and replication are available at: https://github.com/OlaedoOkpareke/Paper2Repository and https://doi.org/10.48152/ssrp-8bs7-7e32' 
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "PUT SOMETHING HERE"
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references2.bib
